HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
abbreviating

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearson correlation HUME scores vs DA for different node types. Struct refers to all structural nodes, P+S are all process and state nodes, H parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}
\end{figure}

>>>>

\begin{figure}[t]
\includegraphics[width=0.45\textwidth]{humevsDAcorrtypes-10en-dero.pdf}
\caption{Pearson correlation HUME scores vs DA for different node types: all
structural nodes (struct), process and state nodes jointly (P+S), parallel
scenes (H), participants (P), centres (C), elaborators (E) and linkers
(L).}
%Struct refers to all structural nodes, P+S are all process and state nodes, H parallel scene nodes, A participant, C centre, E elaborators, and L linker nodes.}
\label{fig:dacorrelationtypes}
\end{figure}
